Out-of-Sample Comparisons of Overfit Models

### 2013-11-04 paper.tex
Clean up and edit notation for the paper

For~\eqref{eq:20}, observe that
\begin{align*}
  \|L(y^{*} -  x_i^{*\prime} \hat{\theta}_{iR}) -
  L(y^{*} - x_i^{*\prime} \hat{\theta}_{iT}) \|_1
  &\leq B_{L} \| x_i^{*\prime} (\hat{\theta}_{iR} - \hat{\theta}_{iT}) \|_2 \\
  &\leq B_{L} \big(\| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 \\
  &\quad+ \| x_i^{*\prime}
  (X_{iR}'X_{iR})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
  \eb_{iR} ] \|_2 \big).
\end{align*}
The first term in the upper bound satisfies
\begin{align*}
  \| x_i^{*\prime} &[(X_{iT}'X_{iT})^{-1} -
  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2^2 =\\
  &= \E \tr\big( x_i^* x_i^{*\prime} X_{iT}'\eb_{iT} \eb_{iT}X_{iT}
   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}]^2 \big) \\
  &\leq \eigen_{K_i}(\E x_i x_i') \E \Big|  \eigen_{K_i}(X_{iT}' \eb_{iT}
  \eb_{iT}' X_{iT}) \sum_{j=1}^{K_i} \eigen_j^2((X_{iR}'X_{iR})^{-1} -
  (X_{iT}'X_{iT})^{-1}) \Big| \\
  &= O(T) \, \Big\| \sum_{j=1}^{t-R} \eigen_j^{-2}(X_{iR}'X_{iR}) \Big\|_{3/2} \\
  &= O(P^2/R)
\end{align*}
The second equality holds because $\eigen_{K_i}(X_{iT}' \eb_{iT}
\eb_{iT} X_{iT}) = O_{L_{3}}(T)$ by assumption and
$(X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}$ has rank $t-R$ with
eigenvalues bounded by those of $(X_{iR}'X_{iR})^{-1}$.

>>>>

For~\eqref{eq:20}, observe that
\begin{align*}
  \|L(y^{*} -  x_i^{*\prime} \hat{\theta}_{iR}) -
  L(y^{*} - x_i^{*\prime} \hat{\theta}_{iT}) \|_1
  &\leq B_{L} P^{-1/2} \| x_i^{*\prime} (\hat{\theta}_{iR} - \hat{\theta}_{iT}) \|_2 \\
  &\leq B_{L} P^{-1/2}\big(\| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 \\
  &\quad+ \| x_i^{*\prime}
  (X_{iR}'X_{iR})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
  \eb_{iR} ] \|_2 \big).
\end{align*}
The first term in the upper bound satisfies
\begin{align*}
  \| x_i^{*\prime} &[(X_{iT}'X_{iT})^{-1} -
  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2^2 =\\
  &= \E \tr\big( x_i^* x_i^{*\prime} X_{iT}'\eb_{iT} \eb_{iT}X_{iT}
   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}]^2 \big) \\
  &\leq \eigen_{K_i}(\E x_i x_i') \E \Big|  \eigen_{K_i}(X_{iT}' \eb_{iT}
  \eb_{iT}' X_{iT}) \sum_{j=1}^{K_i} \eigen_j^2((X_{iR}'X_{iR})^{-1} -
  (X_{iT}'X_{iT})^{-1}) \Big| \\
  &= O(T) \, \Big\| \sum_{j=1}^{t-R} \eigen_j^{-2}(X_{iR}'X_{iR}) \Big\|_{3/2} \\
  &= O(P^2/R)
\end{align*}
The second equality holds because $\eigen_{K_i}(X_{iT}' \eb_{iT}
\eb_{iT} X_{iT}) = O_{L_{3}}(T)$ by assumption and
$(X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}$ has rank $t-R$ with
eigenvalues bounded by those of $(X_{iR}'X_{iR})^{-1}$.
